Temporary Trade Barriers: \\ When Will They End?

### 2016-05-13 presentation.tex
add first three results

\begin{frame}{Why uncertainty?}
\pause
\textbf{Legislature}
\pause
\begin{itemize}
	\item Renews AD duties if $G$ prefers $\tau^{\mathit{ad}}$ to $\tau^a$
\end{itemize}

@@

\begin{frame}{Government}
  $G$ breaks trade agreement if its utility is higher under AD duties than trade agreement tariff
  \begin{itemize}
		\item Preferences are uncertain through $\ta$
	\end{itemize}

	\pause
  \vskip.2in
  Probability that $G$ breaks agreement: \\
	\pause
  \vskip.1in
    $b(e,\tau^a,\tau^{*a},\tau^{\textit{ad}},\ta)$ probability median legislator prefers $\tau^{ad}$ to $\tau^a$ for a given $\ta$ and $e$
\end{frame}

>>>>

\begin{frame}{Why uncertainty?}
\pause
\textbf{Government}
\pause
\begin{itemize}
	\item Renews AD duties if $G$ prefers $\tau^{\mathit{ad}}$ to $\tau^a$
\end{itemize}

@@

\begin{frame}{Government}
  $G$ renews AD duties if its utility is higher under AD duties than trade agreement tariff
  \begin{itemize}
		\item Preferences are ex-ante uncertain through $\ta$
		\pause
		\item When does $G$ renew AD duties? \\
	\pause
  \vskip.1in
    $b(e,\tau^a,\tau^{\textit{ad}})$: probability $G$ prefers $\tau^{ad}$ to $\tau^a$ for a given effort level $e$
\end{itemize}

\pause
\vskip.25in
\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Lemma 1}
  The probability that $G$ renews AD duties is increasing and concave in lobbying effort $e$ $\left(\text{i.e. } \frac{\partial b}{\partial e} \geq 0, \ \frac{\partial^2 b}{\partial e^2} \leq 0  \right)$.
\end{beamerboxesrounded}

\begin{frame}{Home's Trade Agreement Tariff}

\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result 1}
  The total probability that $G$ renews AD duties is decreasing in the home trade agreement tariff $\tau^a$.
\end{beamerboxesrounded}

\vskip.25in
There's both a direct effect and an indirect effect through lobby's incentives, and both are negative:
\[
  \frac{\partial b}{\partial e} \frac{\partial e}{\partial \tau^a} + \frac{\partial b}{\partial \tau^a}
\]
\end{frame}

\begin{frame}{Foreign's Trade Agreement Tariff}

Assuming trading partner does not retaliate
\begin{itemize}
	\item No difference in foreign tariff under AD duty and $\tau^a$. So no effect on $G$'s incentives (either direct or indirect)
\end{itemize}

\vskip.25in
\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result 2}
  The total probability that $G$ renews AD duties is unaffected by foreign's trade agreement tariff $\tau^a$.
\end{beamerboxesrounded}
\end{frame}

\begin{frame}{Profitability of Import-Competing Sector}

Assume $\pi(\cdot)$ shifts up uniformly for all $\tau$.
\begin{itemize}
	\item Convexity of profits $\Rightarrow$ $G$'s marginal benefit of providing protection goes up
	\item Convexity of profits $\Rightarrow$ return from lobbying increases
\end{itemize}

\vskip.25in
\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result 3}
  The total probability that $G$ renews AD duties is increasing in the profitability of the import-competing sector.
\end{beamerboxesrounded}
\end{frame}
